TO FIND

### 2013-05-23 ms.tex
New  results of figure 2

In this section we provide simple simulation results to illustrate the impact of saptial contingencies on species distribution and coexistence. We consider four different landscapes, illustrated at Fig. 1.
with the outcome of simulations using the neutral model. All of these
networks have the same number of nodes (e.g. spatial sampling sites), but both
different number of edges (e.g. dispersal routes between sampling sites) and
patterns of connectivity between nodes. We ask how these differences in
connectivity will shape the emerging properties of the community under the
scenarios represented by each meta-community model. Our analysis is not exhaustive, it is provided simply to illustrate the interaction between metacommunity perspectives and landscape structures on alpha, beta and gamma diversity.

In Fig. 2, we present the species richness of each node of the network (alpha diversity), as a function of
the centrality of the node, under different assumptions of metacommunity
dynamics and network structure. We scaled the species richness by the maximal local species richness to 
facilitate comparison between models. The model parameterization is responsible for differences in both alpha and gamma diversity.  It appears that both in the goeographical and
tree graph, the path dynamics model has a much more considerable variation in local species richness. 
However, in all cases the alpha diversity increases with the node centrality, whether it is
measured by the degree or the eigencentrality. All situations examined give a
remarkably congruent signal.

>>>>

In this section we provide simple simulation results to illustrate the impact of
saptial contingencies on species distribution and coexistence. We consider four
different landscapes, illustrated at Fig. 1,  with the outcome of simulations
using the neutral model. All of these networks have the same number of nodes
(e.g. spatial sampling sites), but both different number of edges (e.g.
dispersal routes between sampling sites) and patterns of connectivity between
nodes. We ask how these differences in connectivity will shape the emerging
properties of the community under the scenarios represented by each
meta-community model. Our analysis is not exhaustive, but is provided simply to
illustrate the interaction between metacommunity perspectives and landscape
structures on alpha, beta and gamma diversity.

In Fig. 2, we present the species richness of each node of the network ($\alpha$
diversity), as a function of the centrality of the node, under different
assumptions of metacommunity dynamics and network structure. We scaled the
species richness by the maximal local species richness to facilitate comparison
between models. The model parameterization is responsible for differences in
both $\alpha$ and $\gamma$ diversity, meaning that only the shape of the
relationship between centrality and richness ought to be looked at.  It appears
that both in the geographical and tree graph, the path dynamics model has a
much more considerable variation in local species richness.  However, in all
cases the alpha diversity increases with the node degree centrality, meaning
that nodes with more connections also host a more diverse community.
Eigen-centrality gave a far less clear-cut result, which can probably be
attributed to the fact that our networks are relatively small in size.
Eigen-centrality reports how well your neighbors are connected, and in graphs
with a short diameter (i.e. the two farthest points are not extremely far
apart), this measure might hold less information.
